---
title: "Eating Out"
author: "Jamal Evans"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Who dines out more often?
There were two years in which the General Social Survey asked about the frequency of eating out. We look at one of them.

The variable name of interest is "eatout."  The URL is https://gss.norc.org/ In GSS data explorer look for "eatout." 

## Find those years 
For the first year the question was asked (1996) we have data. Your assignment is to analyze the GSS yearly data for 1996 and write a statistical report that answers the question.  The data are in the Files section.   

## introduction
$H_0$ There is no difference among the various races with regard to frequency of eating out  
$H_A$ There is a statistical difference between at least two races with rgard to the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
#require(haven)
GSS=read.csv('GSS1996.csv')

```

## Methods
Both 'race' and 'eatout' are categorical. Therefore we use the cat~cat file

### graphical description
```{r}
barchartGC(~eatout + race,data=GSS)
barchartGC(~eatout + race,data=GSS, type="percent")

```

x axis is eatout(1 = yes. 2 = no) labels on the colums are (1=Black, 2 = White, and 3 = other)

###numerical description 
```{r}
table = xtabs(~eatout + race, data=GSS)
print(table)
rowPerc(table)
colPerc(table)
```


## infrential results
The P isquared table test the hypothesis and proves independence between the variables 
### Chi-squared test results
```{r}
chisq.test(table)
chisqtestGC(table)
```

### fisherXY test results
```{r}
fisher.test(table)
fisherXY(GSS$eatout,GSS$race)
```

## Summary and Conclusions

race1 eats out more while 2 and 3 are about the same percentage
0.00038 is not smaller thean .5 so there is no difference between white and black consumers when it comes to eatingOUT




